% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\usepackage[latin1]{inputenc}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\normalsize {\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\resdescription} [1] {}
\usepackage{hyperref}


%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Peter Kerpedjiev}  & +43 680 401 3012\\
Pezzlgasse 47/21-22 &  pkerpedjiev@gmail.com \\
1170 Vienna & \url{http://emptypipes.org/about}\\
Austria \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\hrule
\begin{itemize}
\item
	\ressubheading{University of Vienna}{Vienna, Austria}{PhD, Student, Bioinformatics}{October 2011 - }
	\vspace{10pt}
	
	\textbf{Tentative Thesis:} \textit{RNA Tertiary Structure Prediction and Visualization}
\item
	\ressubheading{University of Copenhagen}{Copenhagen, Denmark}{M.Sc. Bioinformatics}{Sep. 2009 - August 2011}
	\vspace{10pt}
	
	\textbf{Thesis:} \textit{Using Position Specific Scoring Matrices for Short Read Alignment on a Compressed Genome 
	Index}
\item

	\ressubheading{University of British Columbia}{Vancouver,
          Canada}{B.Sc. Computer Science and Biology}{Sep. 2003 -
          May. 2006}

     
\end{itemize}


\resheading{Skills / Interests}
\hrule
\begin{description}\setlength{\itemsep}{-1mm}
\item[Spoken Languages:] English (native), Bulgarian (fluent), German (working)
\item[Programming Languages:] C, Python, Javascript, C\#, R, Java
\item[Databases:] PostgreSQL, Oracle, MS SQL Server
\item[Bioinformatics:] Short-read alignment, Next Generation Sequencing (NGS), Protein structure prediction, RNA structure prediction, Molecular Modelling
\end{description}

\resheading{Professional Experience}
\hrule
\begin{itemize}
\item
	\ressubheading{Bayer Technology Services}{Leverkusen, Germany}{Intern, Systems Biology}{June 2010 - September 2010}

	
\item
	\ressubheading{Bioinformatics Center, University of Copenhagen}{Copenhagen, Denmark}{Research Assistant, Short Read Alignment}{February 2010 - June 2010}

\item
	\ressubheading{McKesson Corporation}{Seattle, WA (USA)}{Software Engineer,
          Patient Records Group}{June 2006 - July 2009}
\item
  \ressubheading{Carnegie Mellon University}{Pittsburgh, PA (USA)}{Programmer, Universal Speech Interface Project}{Summer 2000, Summer 2001}
\end{itemize}

\resheading{Teaching Experience}
\hrule
\begin{itemize}
\item
  \ressubheading{Max F. Perutz Laboratories}{Vienna, Austria}{Teaching Assistant,
    Grundlagen der Bioinformatik}{June 2014, December 2014, April 2015}
\end{itemize}

\resheading{Other Experience}
\hrule
\begin{itemize}
\item
  \ressubheading{UBC Bioinformatics Center}{Vancouver, Canada}{Volunteer 
  Programmer,
    Atlas Data Warehouse Project}{January 2006 - May 2006}

\end{itemize}

\resheading{Open Source Software}
\hrule
\begin{itemize}
  \item \textbf{forna} {An online tool for displaying the secondary structure of RNA. (\url{http://rna.tbi.univie.ac.at/forna})} 
   \item \textbf{forgi} {A python library for annotating and manipulating RNA secondary and tertiary structure. (\url{http://www.tbi.univie.ac.at/~pkerp/forgi/})} 
  \item \textbf{bwa-pssm} {A short read aligner using position-specific scoring matrices to encode the error probabilities for each base. (\url{http://bwa-pssm.binf.ku.dk/})}
\end{itemize}
\resheading{Scholarships / Awards}
\hrule
\begin{itemize}
  \item
  \ressubheading{BioVis Design Contest}{Dublin, Ireland}{Honorable Mention - ``DotStruct - An Improved Dot-Plot''}{July 2015}
  
\item
  \ressubheading{Novo Scholarship 2011}{Copenhagen, Denmark}{Support for Master's Thesis Work}{February 2011 - August 2011}

 \end{itemize}
\resheading{Publications}
\hrule
\begin{itemize}
   \item
	Kerpedjiev, P., Hammer S., Hofacker I. (2015). Forna (force-directed RNA): Simple and effective online RNA secondary structure diagrams. \textit{Bioinformatics}, 31(20), 3377-9.
	
  \item
	Kerpedjiev, P., H{\"o}ner zu Siederdissen C., Hofacker I. (2015). Predicting RNA 3D structure using a coarse-grain helix-centered model. \textit{RNA}, 21.6, 1110-1121.

\item
	Kerpedjiev, P., Frellsen, J., Lindgreen, S., \& Krogh, A. (2014). Adaptable probabilistic mapping of short reads using position specific scoring matrices. \textit{BMC bioinformatics}, 15(1), 100.

\item
	Jakobsen, T. H., ... \& Bjarnsholt, T. (2013). Complete genome sequence of the cystic fibrosis pathogen Achromobacter xylosoxidans NH44784-1996 complies with important pathogenic phenotypes. \textit{PloS one}, 8(7), e68484.
  
\end{itemize}

\resheading{Selected Oral Presentations}
\hrule
\begin{itemize}
  \item
  \ressubheading{ISMB / ECCB Bioinformatics Open Source SIG}{Dublin, Ireland}{Simple, Shareable, Online RNA Secondary Structure Diagrams}{July 2015}
  
  \item
  \ressubheading{Vienna RNA Community Retreat}{Retz, Austria}{Visualizing Co-Transcriptional Folding}{April 2015}
 
  \item
  \ressubheading{TBI Winter Seminar}{Bled, Slovenia}{Super Simple Software for Showing Secondary Structure}{February 2015}
 
  \item
  \ressubheading{Herbstseminar der Bioinformatik}{Doubice, Czech Republic}{RNA Secondary Structure Visualization Using D3.js}{October 2014} 
   
 \end{itemize}
 
 \resheading{Selected Posters}
\hrule

\begin{itemize}

\item
  \ressubheading{RNA Regulation of the Genome SFB Hearing}{Vienna, Austria}{From 2D to 3D: RNA Structure Prediction}{October 2014}

\item
  \ressubheading{{\"O}GBMT Meeting}{Vienna, Austria}{RNA in 3D: Sequence to Tertiary Structure Using a Simplified Representation}{September 2014}  

\item
  \ressubheading{ISMB}{Berlin, Germany}{Adaptable Probabilistic Short Read Alignment Using Position Specific Scoring}{July 2013}  
    
 

  

\end{itemize}

\end{document}
